Tuning Low Frequency Pulsar Searching with an Artificial Pulsar Device

### 2020-11-28 ms.tex
new file:   dm0_profile.pdf 	new file:   dm10_profile.pdf 	new file:   dm1_profile.pdf 	modified:   ms.tex

\usepackage{newtxtext,newtxmath}
\usepackage[T1]{fontenc}
\DeclareRobustCommand{\VAN}[3]{#2}
\let\VANthebibliography\thebibliography
\def\thebibliography{\DeclareRobustCommand{\VAN}[3]{##3}\VANthebibliography}
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
%\usepackage{amssymb}	% Extra maths symbols

@@

>>>>

\usepackage{newtxtext,newtxmath}
\usepackage[T1]{fontenc}
\DeclareRobustCommand{\VAN}[3]{#2}
\let\VANthebibliography\thebibliography
\def\thebibliography{\DeclareRobustCommand{\VAN}[3]{##3}\VANthebibliography}
\usepackage{graphicx}	% Including figure files
\usepackage{pict2e}
\usepackage{amsmath}	% Advanced maths commands
%\usepackage{amssymb}	% Extra maths symbols

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\columnwidth]{dm0_profile.pdf}
    \caption{Frequency dependent pulse profile before the dispersion effect is applied. 
    The period is set to be 20 ms and the amplitude profile is described a gaussian function with $\sigma=0.05$}
    \label{fig:dm0_profile}
 \end{figure}

 \begin{figure}
    \centering
    \includegraphics[width=0.9\columnwidth]{dm10_profile.pdf}
    \caption{Frequency dependent pulse profile with a $DM=10$ dispersion effect applied. The parameter of the pulsar
    is same as the one used in Figure \ref{fig:dm0_profile}}
    \label{fig:dm10_profile}
 \end{figure}
